|

### 2025-03-13 docs/presentation.qmd
slide deck update

suppressMessages({
  library(tidyverse)
  library(gt)
  library(kableExtra)
  library(modelsummary)
  library(showtext)

  devtools::source_url(
    "https://raw.githubusercontent.com/trr266/treat/main/code/R/theme_trr.R"
  )
})

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv(
	"../data/external/invited_authors_anon.csv", show_col_types = FALSE
)

@@

@@

## Motivation

@@

Survey of authors that published in top six accounting journals over the period 2016-2021

Descriptive Research Questions (relative to general social science results)

- How do accountants assess the reproducibility of influential accounting work?
- How do they perceive and use two prominent open science approaches to promote reproducibility:
	- Public sharing of research materials (i.e., data, code, and procedures)
	- Pre-registration of study designs

Experimental Question: Is the stated willingness to share research materials ...

- ... affected by the rationale (collaboration versus control) and/or
- ... affected by the scope (public or private sharing) of the sharing request?

## Invitation Email

## Sample Composition

@@

## Geographical Response Representation

@@

## Reproducibility Assessed Across the Social Sciences

@@

@@

@@

## Experimental Findings on Sharing Determinants

@@

## Rationales for/against Sharing: Some Quotes

```{r, asis = TRUE}

quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
df <- sd %>%
 	filter(row_number() %in% quotes) %>%
 	transmute(
 		Condition = sprintf(
 			"%s/%s", ifelse(exp_tment_collab, "Collab", "Control"),
 			ifelse(exp_tment_private, "Private", "Public")
 		),
 		Quote = exp_reflect
 	)

gt(df) %>% 
	cols_width(
		`Condition` ~ pct(15),
		`Quote` ~ pct(85)
	) %>%
	tab_options(table.font.size = 7) %>%
	as_latex() %>%
	tiny_size()
```

## Observational Data on Sharing Behavior: Author Level

## Observational Data on Sharing Behavior: Journal Level

<!---
## Pre-Registration: Awareness Across the Social Sciences

```{r Tab10aPreRegAwareSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_heard", "demog_discipline", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```
--->

## Pre-Registration: Familiarity by Method

## Pre-Registration: Usage by Method

## Pre-Registration: Trust Effect by Method

@@

- We are skeptical about the reproducibility of our work and at the same time
- somewhat behind the curve with regards to research material sharing and pre-registration

@@

## Taking stock... It might not be as bad as we think!

@@

## Reproducibility Across Methods

@@

>>>>

suppressMessages({
  library(tidyverse)
  library(gt)
  library(kableExtra)
  library(modelsummary)
  library(showtext)
	library(tufte)
  devtools::source_url(
    "https://raw.githubusercontent.com/trr266/treat/main/code/R/theme_trr.R"
  )
})

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv(
	"../data/external/invited_authors_anon.csv", show_col_types = FALSE
)

@@

create_quote <- function(idval) {
	obs <- sd %>% filter(id == idval)
	tment_str <- paste0(
		ifelse(obs$exp_tment_control == 1, "Control", "Collab"), "/",
		ifelse(obs$exp_tment_private == 1, "Private", "Public")
	) 
	paste(obs$exp_reflect, "\\\\", quote_footer(paste("---", tment_str)))
}

@@

## Motivation: Estimating The Reproducibility of Psychological Science

\begin{center}
\includegraphics[height =0.7\textheight]{"materials/osc_2015.jpeg"} \\
Open Science Collaboration (2015, Science)
\end{center}

## Motivation: 1,500 Scientists Lift the Lid on Reproducibility

\begin{center}
\includegraphics[height =0.7\textheight]{"materials/baker_2016.jpeg"} \\
Baker (2016, Nature)
\end{center}

## Motivation: Survey of OS Practices and Attitudes in the Social Sciences

@@

Survey of authors that published in top six accounting journals over the period 2016-2021 to address three research questions:

1.  How does the accounting research community assess the reproducibility of their influential work?

2.  What are the views of the accounting research community about research material sharing and pre-registration, two prominent open science methods to increase the reproducibility of research?

3.  What are the (perceived) costs and benefits of research material sharing?

## Theoretical Framework

The acts of research material sharing and pre-registration can be understood as voluntary disclosure decisions.

- **Lack of unravelling**: Non-trivial direct costs and researchers might be unaware of their research' quality
- **Substantial indirect costs**: Competetive effects and reputational concerns
- **Limited private benefits**: Researchers are incentivized by publication success and less by research quality per se
- **Positive externalities**: Activities are likely to benefit other researchers without direct compensation for acting researcher (but: 'warm glow')

## Sample Composition {#sample}

@@

\placebutton{skip}{email}{invitation email}

## Representativeness by Geographical Region

@@

## Representativeness by Field

```{r FigureRespField, fig.width=12, fig.height=6, fig.align="center", fig.showtext = TRUE}
byu_fields_comp(byu, sd)
```

## Representativeness by Method

```{r FigureRespMethod, fig.width=9, fig.height=4.5, fig.align="center", fig.showtext = TRUE}
byu_methods_comp(byu, sd)
```

## Reproducibility Assessed Across the Social Sciences {#reproducibility}

@@

\placebutton{skip}{terminology}{Terminology}

@@

<!---
## Pre-Registration: Familiarity by Method

--->

## Pre-Registration: Usage by Method {#preregmethod}

\placebutton{skip}{preregtrust}{trust in pre-registration by method}

## Observational Data: Author Level

## Observational Data: Journal Level

@@

## Costs and Benefits of Research Material Sharing: Experimental Findings

@@

## Quotes about Sharing Benefits: Helping Others
\begin{quote}
`r create_quote(295)`
\end{quote}
\vspace{1cm}
\begin{quote}
`r create_quote(403)`
\end{quote}

## Quotes about Sharing Benefits: Helping Yourself

\begin{quote}
`r create_quote(249)`
\end{quote}
\vspace{1cm}
\begin{quote}
`r create_quote(186)`
\end{quote}

## Quotes about Sharing Costs: Direct Costs

\begin{quote}
`r create_quote(154)`
\end{quote}

## Quotes about Sharing Costs: Valuable Intellectual Property

\begin{quote}
`r create_quote(47)`
\end{quote}

## Quotes about Sharing Costs: Unethical Usage Concerns

\begin{quote}
`r create_quote(169)`
\end{quote}

## Quotes about Sharing Benefits/Costs: Depends on Researcher

\begin{quote}
`r create_quote(317)`
\end{quote}

@@

- We are skeptical about the reproducibility of our work and at the same time
- somewhat behind the curve with regards to research material sharing and pre-registration.

Our findings suggest that weighting direct and indirect costs higher than private and public benefits might be a rationale for this behavior.

@@

## Taking stock: Distributions of Test Statistics in Archival Accounting Studies

\begin{center}
\includegraphics[height =0.7\textheight]{"materials/chang_gao_li_2025.jpeg"} \\
Chang, Gao, and Li (2025, JAR)
\end{center}

## Taking stock: Relatively speaking...

@@

## Taking stock: Reproducibility Across Methods

@@

# Backup

## Invitation Email {#email}

\placebutton{return}{sample}{Return}

## Some Terminology (Dreber and Johannesson, 2024) {#terminology}

Types of reproducibility:

- **Computational reproducibility**: Results of original study can be reproduced based on data and code posted or provided by the original authors.	
- **Recreate reproducibility**:	Results of original study can be reproduced based on the information in the paper and access to the same raw data source.	
- **Robustness reproducibility**:	Results og original study are robust to alternative reasonable analytical decisions on the same data.

Types of replicability:

- **Direct replicability**:	Results of original studies can be repeated on new data using the same research design and analysis as the original study.	
- **Conceptual replicability**:Results of original study can be repeated on new data using an alternative research design and/or analysis to test the same hypothesis.

\placebutton{return}{reproducibility}{Return}

## Pre-Registration: Trust Effect by Method {#preregtrust}

\placebutton{return}{preregmethod}{Return}
